---
title: "Final Project R Markdown"
author: "Wendy Lee"
date: "`r Sys.Date()`"
output: html_document

---
# Introduction
This dataset is a simulation of de-identified data from the EPIC electronic health record system. In particular, it contains pediatric hospitalization data of children under 3 years of age in the United States. Variables included in this preliminary analysis include age, sex, race, hemoglobin levels, census region, and length of hospital stay.

# Analytic Goals
* Understand the prevalence of anemia among hospitalized children under 3 year old
* Understand the distribution of demographic characteristics in this sample

# Analysis Objectives 
Data cleaning, data manipulation, and basic exploratory analysis of demographic and clinical variables will be included in this report

```{r, set-chunk-options}
#| echo= FALSE
library(knitr)
opts_chunk$set(
  echo= FALSE
)
```

```{r, read-data, include=FALSE}
here::i_am("Untitled.Rmd")
data<- 
  readRDS(
    file=here::here("output/dataclean.rds")
  )
```

# Demographic Information
Characteristics of 1000 pediatric patients are shown in Table 1. 
```{r, table1}
table1<-readRDS(
  file=here::here("output/table1.rds")
)
table1
```

# Regression Analysis

## Linear Model

In this analysis, we use hemoglobin as a continuous outcome variable
```{r, regressionmodel}
#linear model

both_models<-readRDS(
  file= here::here("output/both_models.rds")
)

both_tables<-readRDS(
  file= here::here("output/both_tables.rds")
)

both_tables$primary #model from primary table 


```
## Logistic Model

In this analysis, we generated a binary outcome where level 1 of the outcome means the hemoglobin level was greater than 11
```{r, logisticmodel}

both_tables$secondary 

```


# Graphical Analysis

Below we report a scatter plot of hemoglobin levels as a function of number of hospitalizations. 

```{r, plot-data}
#| fig.align="center",
#| out.width="600px"

knitr::include_graphics(
  here::here("output/scatter.png")
)

```

